---
title: "LINCS CDS2 genesets for PCxN"
output: html_notebook
---

```{r eval=FALSE, include=FALSE}
Sys.setenv(TZ='GMT')

cds_meta_all <- read.csv("~/Kat/Documents/Databases/LINCSCDS2/analysis/all_metadata.tsv", sep="\t")
cds_meta_sig <- read.csv("~/Kat/Documents/Databases/LINCSCDS2/analysis/sigmetadata_lincsCD.tsv", sep="\t")

probe_id_values <- readr::read_delim("~/Kat/Documents/Databases/LINCSCDS2/analysis/signature_probe_gene.tsv", delim="\t", col_names=FALSE)
colnames(probe_id_values) <- c("_id", "chdir", "pr_id", "pr_gene_symbol", "pr_gene_id")

cds_pvals <- read.csv("~/Kat/Documents/Databases/LINCSCDS2/analysis/pvals_cds2.txt")
cds_id_pvals <- read.csv("~/Kat/Documents/Databases/LINCSCDS2/analysis/sig_id_pval_cds2.txt", sep=" ")
```
info on brd ids: https://clue.io/connectopedia/what_is_a_brd_id
```{r}
#check how many signatures are significant per cell type
cell_sig_freq <- as.data.frame(table(cds_meta_sig$cell_id))
cell_all_freq <- as.data.frame(table(cds_meta_all$cell_id))



cell_freq <- dplyr::left_join(cell_all_freq, cell_sig_freq, by="Var1")
colnames(cell_freq) <- c("cell_type", "total_sig", "signif_sig")
```

```{r eval=FALSE, include=FALSE}
# ```{r}
hist(cds_meta_sig$pvalue)
# hist(as.numeric(pvals$pval))

library(ggplot2)
library(dplyr)
sort(table(cds_meta_sig$cell_id), decreasing = T) #number of signatures per cell line
head(sort(table(cds_meta_sig$pert_id), decreasing = T), 50) #number of signatures per most popular perts

length(unique(cds_meta_sig$pert_id))
length(unique(cds_meta_sig$cell_id))

#save it into a table
cell_meta <- as.data.frame(t(sort(table(cds_meta_sig$cell_id), decreasing = T)))
rownames(cell_meta) <- cell_meta$Var2
cell_meta <- cell_meta[,-1]
colnames(cell_meta) <- c("cell_line", "sig")

cell_meta_all <- as.data.frame(t(sort(table(cds_meta_all$cell_id), decreasing = T)))
rownames(cell_meta_all) <- cell_meta_all$Var2
cell_meta_all <- cell_meta_all[,-1]
colnames(cell_meta_all) <- c("cell_line", "all")

cell_meta <- dplyr::left_join(cell_meta_all, cell_meta, by="cell_line")
cell_meta$prop <- round(cell_meta$sig/cell_meta$all, 4)

library(reshape)
data.m <- melt(cell_meta, id.vars='cell_line')

ggplot(data.m, aes(cell_line, value)) +   
  geom_bar(aes(fill = variable), position = "dodge", stat="identity")

ggplot(cell_meta, aes(cell_line, sig, all, fill = sig)) +
  geom_bar(stat = "identity")

plot(cell_meta$all, cell_meta$prop)

data.m <- data.m[order(data.m$value), ]

ggplot(data=data.m, aes(x=cell_line, y=value, fill=variable)) +
    geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

sort(table(cds_meta_all$cell_id))
```


```{r eval=FALSE, include=FALSE}
# gene_ids <- unlist(mget(probe_id_values$pr_id, hgu133aENTREZID, ifnotfound = NA))
#pr_gene_id is an entrez id, so the genesets can be automatically converted into gene lists
#the given gene-ids are better mapped than with mget-hgu133aENTREZID

probe_id_values$up <- probe_id_values$chdir > 0
probe_id_values$down <- probe_id_values$chdir < 0


#need to remove all the -666 and the duplicated entrez ids --- ask sokratis what happens if the same entrez id is put in more than twice.

probe_id_values <- probe_id_values[probe_id_values$pr_gene_id != -666, ]

probe_id_values_up <- probe_id_values[probe_id_values$up == TRUE, ]
probe_id_values_down <- probe_id_values[probe_id_values$down == TRUE, ]

####split the entrez ids /// UP GENES --- get a list of lists
tosplit <- probe_id_values_up[grep("///", probe_id_values_up$pr_gene_id),]
tosplit <- unique(tosplit[,c("_id", "pr_gene_id")])
# tosplit$split <- NA
x <- list()
for (i in 1:nrow(tosplit)) {
# n <- 100
# tosplit <- tosplit[1:n, ]
# for (i in 1:n) {
  # tosplit$split[i] <- strsplit(tosplit$pr_gene_id[i], "///")
  x[i] <- strsplit(tosplit$pr_gene_id[i], "///")
  names(x)[i] <- tosplit$`_id`[i] #need to concatenate them to other signatures or could make a dataframe for combining to the rest later 
}
x[[1]] == tosplit$split[[1]]

#get the total number of rows required for the data frame that will have each gene as separate row
sum(lengths(tosplit$split))
sum(lengths(x))

#make a dataframe that has one gene and it's sig id per row
split_data <- data.frame(matrix(ncol=7, nrow = sum(lengths(x))), row.names = 1:sum(lengths(x)))
colnames(split_data) <- colnames(probe_id_values_up)
split_data$up <- TRUE
split_data$down <- FALSE
n <- 1
for (i in 1:(length(x))) {
  for (j in 1:(length(x[[i]]))){
    split_data$`_id`[n] <- names(x)[i]
    split_data$pr_gene_id[n] <- x[[i]][j]
    n <- n+1
  }
}
split_data <- unique(split_data)
probe_id_values_up_ <- rbind(probe_id_values_up, split_data)


#######################

####split the entrez ids /// DOWN GENES
tosplit <- probe_id_values_down[grep("///", probe_id_values_down$pr_gene_id),]
tosplit <- unique(tosplit)
x <- list()
tictoc::tic()
for (i in 1:nrow(tosplit)) {
# for (i in 1:100) {
  x[i] <- strsplit(tosplit$pr_gene_id[i], "///")
  names(x)[i] <- tosplit$`_id`[i] #need to concatenate them to other signatures or could make a dataframe for combining to the rest later 
}
tictoc::toc()


#get the total number of rows required for the data frame that will have each gene as separate row
sum(lengths(x))

tictoc::tic()
split_data <- data.frame(matrix(ncol=7, nrow = sum(lengths(x))), row.names = 1:sum(lengths(x)))
colnames(split_data) <- colnames(probe_id_values_down)
split_data$down <- TRUE
split_data$up <- FALSE
n <- 1
for (i in 1:(length(x))) {
  for (j in 1:(length(x[[i]]))){
    split_data$`_id`[n] <- names(x)[i]
    split_data$pr_gene_id[n] <- x[[i]][j]
    n <- n+1
  }
}
tictoc::toc()
split_data <- unique(split_data)
probe_id_values_down_ <- rbind(probe_id_values_down, split_data)
```

putting in the right format
```{r eval=FALSE, include=FALSE}

#put it in the right format the UP gene sets
probe_id_values_up__ <- probe_id_values_up_[, c("_id", "pr_gene_id")]
# probe_id_values_up_ <- probe_id_values_up[1:10000, c("_id", "pr_gene_id")]
probe_id_values_up__ <- aggregate(probe_id_values_up__, list(probe_id_values_up__$`_id`), FUN=c)
up.gs <- (apply(probe_id_values_up__, 1,  function(a){(a$"pr_gene_id")}))
names(up.gs) <- as.character(unique(unlist(probe_id_values_up__$"_id"))) #change to a different naming, more meaninghful system

#put it in the right format the DOWN gene sets
probe_id_values_down__ <- probe_id_values_down_[, c("_id", "pr_gene_id")]
# probe_id_values_down_ <- probe_id_values_down[1:10000, c("_id", "pr_gene_id")]
probe_id_values_down__ <- aggregate(probe_id_values_down__, list(probe_id_values_down__$`_id`), FUN=c)
down.gs <- (apply(probe_id_values_down__, 1,  function(a){(a$"pr_gene_id")}))
names(down.gs) <- as.character(unique(unlist(probe_id_values_down__$"_id"))) #change to a different naming, more meaninghful system



# probe_id_values_up_1000 <- probe_id_values_up[1:1000,]
# 
# up.gs <- list()
# names(up.gs) <- unique(probe_id_values_up$`_id`)
# up.gs <- apply(probe_id_values_up_1000, 1, function(x){unique(as.character(x))})
# 
# 
# GeneSigDB.Hs.gs <- sapply(genesigdbEntrez, function(x){unique(as.character(na.omit(x@geneIds)))})
# 
# # Extract names
# names(GeneSigDB.Hs.gs) <- sapply(genesigdbEntrez, function(x){x@setName})
# 
# # limit to minimum of 5 genes
# GeneSigDB.Hs.gs <- GeneSigDB.Hs.gs[
# lapply(GeneSigDB.Hs.gs, length) >= 5]
# length(GeneSigDB.Hs.gs)
```

```{r}
# save(up.gs, file ="LINCScds.up.gs")
# save(down.gs, file="LINCScds.down.gs")
load("LINCScds.up.gs")
load("LINCScds.down.gs")

down.gs_ <- down.gs
up.gs_ <- up.gs

up.gs__ <- lapply(up.gs_, function(x){x[grep("//", x, invert = TRUE)]})
up.gs__ <- lapply(up.gs__, function(x){unique(x)})
up.gs.len <- lengths(up.gs__)
mean(up.gs.len)
median(up.gs.len)
hist(up.gs.len)
sum(up.gs.len < 5)
small_gs <- names(up.gs.len)[up.gs.len < 5] #names to be removed
length(small_gs)

down.gs__ <- lapply(down.gs_, function(x){x[grep("//", x, invert = TRUE)]})
down.gs__ <- lapply(down.gs__, function(x){unique(x)})
down.gs.len <- lengths(down.gs__)
mean(down.gs.len)
median(down.gs.len)
hist(down.gs.len)
sum(down.gs.len < 5)
small_gs <- unique(c(small_gs, names(down.gs.len)[down.gs.len < 5])) #names to be removed
length(small_gs)

min_gs <- 5
sum(down.gs.len < min_gs)
sum(up.gs.len < min_gs)
length(small_gs)
#filter out the small gene sets
# sum(cds_meta_sig$X_id %in% small_gs)
# cds_meta_sig_big <- cds_meta_sig[!cds_meta_sig$X_id %in% small_gs,]
# 
# cds_meta_sig <- cds_meta_sig_big

# filter down the up.gs and the down.gs --- anyway you want
```
filter down the up.gs and the down.gs --- anyway you want

There are a lot of replicates in signatures, check the overlap between them
```{r eval=FALSE, include=FALSE}
colnames(cds_meta_sig)
cds_meta_batch <- cds_meta_sig %>% dplyr::select(cell_id, pert_dose_unit, pert_id, pert_time, pert_time_unit, pert_type) %>% arrange(cell_id, pert_dose_unit, pert_id, pert_time, pert_time_unit, pert_type) %>% unique



```


filtering down the numbers
```{R eval=FALSE, include=FALSE}
##filtering down the numbers of gene sets, because no specific requirenments for this run
min_gs <- 5
sum(down.gs.len < min_gs)
small_gs <- unique(c(small_gs, names(down.gs.len)[down.gs.len < min_gs])) #names to be removed
length(small_gs)
#filter out the small gene sets
sum(cds_meta_sig$X_id %in% small_gs)
cds_meta_sig_big <- cds_meta_sig[!cds_meta_sig$X_id %in% small_gs,]

cds_meta_sig <- cds_meta_sig_big


#filter to one pert_time
table(cds_meta_sig$pert_time)
drug_time <- cds_meta_sig_big[cds_meta_sig$pert_time == 6,]
table(drug_time$pert_time)


#filter to pert_dose values that have at least 10 samples
table(drug_time$pert_dose_unit)
sort(table(drug_time$pert_dose))
drug_dose <- drug_time[drug_time$pert_dose %in% names(sort(table(drug_time$pert_dose), decreasing = T))[sort(table(drug_time$pert_dose), decreasing = T)>10],]
sort(table(drug_dose$pert_dose))


#filter to the most popular cell types
sort(table(drug_dose$cell_id), decreasing = T)
drug_cell <- drug_dose[drug_dose$cell_id %in% names(sort(table(drug_dose$cell_id), decreasing = T))[sort(table(drug_dose$cell_id), decreasing = T)> 500],]
sort(table(drug_cell$cell_id), decreasing = T)
drug_cell <- droplevels(drug_cell)

#filter to the most popluar drugs
sort(table(drug_cell$pert_id), decreasing = T)[1:150]
drug_drug <- drug_cell[drug_cell$pert_id %in% names(sort(table(drug_cell$pert_id), decreasing = T))[sort(table(drug_cell$pert_id), decreasing = T)> 4],]
sort(table(drug_drug$pert_id), decreasing = T)[1:500]
sort(table(drug_drug$pert_time), decreasing = T)
sort(table(drug_drug$pert_dose), decreasing = T)
sort(table(drug_drug$cell_id), decreasing = T)

#check what is left
table(droplevels(drug_drug$pert_id), droplevels(drug_drug$cell_id))

length(unique(droplevels(drug_drug$pert_id))) #number of different drugs
nrow(drug_drug)


# drug_names <- (names((sort(table(cds_meta_sig$pert_id), decreasing = T)))[1:1500])
# sort(rowSums(table(cds_meta_sig$cell_id[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))) #how many samples per cell line if we only look at the top 1500 drugs
# sort(rowSums(table(cds_meta_sig$pert_dose[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))) #how many samples per concentration if we only look at the top 1500 drugs
# 
# 
# drug_cell <- as.data.frame(table(cds_meta_sig$cell_id[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))

#L1000CDS2.up.sig_id

```

### filtering down the number of gene sets for Rheumatoid Arthritis study
```{R eval=FALSE, include=FALSE}
blood_cell_types <- c("NOMO1", "THP1", "U937", "PL21", "SKM1", "WSUDLCL2")
neuro_cell_types <- c("NEU", "NPC")
skin_cell_types <- c(
                    # "A375", 
                     "SKMEL28", "SKMEL1")

cell_types <- c(blood_cell_types, neuro_cell_types, skin_cell_types)


neuroprotective <- read.csv("~/Google Drive/Documents/Parkinsons/translated_drug_list_neuroprotective.csv")
PD_dugs <- read.csv("~/Google Drive/Documents/Parkinsons/translated_drug_list_PD.csv")
AD_drugs <- read.csv("~/Google Drive/Documents/KATdb_shiny/translated_drug_list_AD.csv")
RA_drugs <- read.csv("~/Google Drive/Documents/Rheumatoid Arthritis/RA2019/translated_drug_list_RA.csv")
drug_list <- rbind(neuroprotective, PD_dugs, AD_drugs, RA_drugs)
drug_list <- drug_list[!duplicated(drug_list$target_name) & !is.na(drug_list$target_name),]
drug_list <- drug_list$target_name
length(drug_list)

##filtering down the numbers of gene sets for RA study

##get the cell types required and the drugs to add to a random selection
#filter to selected cell types
x <- cds_meta_sig
sort(table(x$cell_id), decreasing = T)
drug_cell_seed <- x[x$cell_id %in% cell_types,]
sort(table(drug_cell_seed$cell_id), decreasing = T)
sum(table(drug_cell_seed$cell_id))
drug_cell_seed <- droplevels(drug_cell_seed)
x <- drug_cell_seed
sort(table(x$pert_id), decreasing = T)[1:100]
sort(table(x$pert_time), decreasing = T)
sort(table(x$pert_dose), decreasing = T)
sort(table(x$cell_id), decreasing = T)


#filter to drugs of interest
x <- cds_meta_sig
nrow(x[x$pert_id %in% drug_list,])
sort(table(x$pert_id), decreasing = T)[1:150]
drug_drug_seed <- x[x$pert_id %in% drug_list,]
sum(table(drug_drug_seed$pert_id))
x <- drug_drug_seed
sort(table(x$pert_id), decreasing = T)[sort(table(x$pert_id), decreasing = T)>0]
sort(table(x$pert_time), decreasing = T)
sort(table(x$pert_dose), decreasing = T)
sort(table(x$cell_id), decreasing = T)[sort(table(x$cell_id), decreasing = T)>0]
table(x$cell_id[x$cell_id%in%cell_types])[table(x$cell_id[x$cell_id%in%cell_types])>0]

#join seeded dfs
seed_samp <-  unique(rbind(drug_cell_seed, drug_drug_seed))
x <- seed_samp
sort(table(x$pert_id), decreasing = T)[sort(table(x$pert_id), decreasing = T)>5]
sort(table(x$pert_time), decreasing = T)
sort(table(x$pert_dose), decreasing = T)
sort(table(x$cell_id), decreasing = T)[sort(table(x$cell_id), decreasing = T)>0]


##get a random selection
#filter to the most popular cell types
x <- cds_meta_sig
sort(table(x$cell_id), decreasing = T)
drug_cell <- x[x$cell_id %in% names(sort(table(x$cell_id), decreasing = T))[sort(table(x$cell_id), decreasing = T)> 2000],]
drug_cell <- droplevels(drug_cell)
sort(table(drug_cell$cell_id), decreasing = T)


#filter to most popular pert_time
x <- drug_cell
table(x$pert_time)
drug_time <- x[x$pert_time %in% c(24),]
table(drug_time$pert_time)
sum(table(drug_time$pert_time))

#filter to pert_dose values that have at least 10 samples and be at least 1um
x <- drug_time
table(x$pert_dose_unit)
sort(table(x$pert_dose))
x <- x[x$pert_dose > 1,]
drug_dose <- x[x$pert_dose %in% names(sort(table(x$pert_dose), decreasing = F))[sort(table(x$pert_dose), decreasing = F)>20],]
sort(table(drug_dose$pert_dose))
sum(table(drug_dose$pert_dose))

#filter to the most popluar drugs
x <- drug_dose
sort(table(x$pert_id), decreasing = T)[1:150]
drug_drug <- x[x$pert_id %in% names(sort(table(x$pert_id), decreasing = T))[sort(table(x$pert_id), decreasing = T)> 5],]
sort(table(drug_drug$pert_id), decreasing = T)[1:20]
sort(table(drug_drug$pert_time), decreasing = T)
sort(table(drug_drug$pert_dose), decreasing = T)
sort(table(drug_drug$cell_id), decreasing = T)
sum(table(drug_drug$pert_id))

#check what is left
table(droplevels(drug_drug$pert_id), droplevels(drug_drug$cell_id))
sum(table(drug_drug$pert_id))
length(unique(droplevels(drug_drug$pert_id))) #number of different drugs
nrow(drug_drug)

drug_drug$experiment_id <- sub("([0-9]):.*", "\\1", drug_drug$sig_id) 
sort(table(drug_drug$experiment_id), decreasing = T)[1:20]

#join with seed 
seed_samp$experiment_id <- sub("([0-9]):.*", "\\1", seed_samp$sig_id) 
sort(table(seed_samp$experiment_id), decreasing = T)[1:20]
selected_drug <- unique(rbind(seed_samp, drug_drug))
selected_drug <- unique(selected_drug[order(selected_drug$X_id),])
nrow(selected_drug)


# drug_names <- (names((sort(table(cds_meta_sig$pert_id), decreasing = T)))[1:1500])
# sort(rowSums(table(cds_meta_sig$cell_id[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))) #how many samples per cell line if we only look at the top 1500 drugs
# sort(rowSums(table(cds_meta_sig$pert_dose[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))) #how many samples per concentration if we only look at the top 1500 drugs
# 
# 
# drug_cell <- as.data.frame(table(cds_meta_sig$cell_id[cds_meta_sig$pert_id %in% drug_names], cds_meta_sig$pert_id[cds_meta_sig$pert_id %in% drug_names]))

#L1000CDS2.up.sig_id
```
rename the genesets

subset the gene sets only on the ones we want. 
```{r eval=FALSE, include=FALSE}
#keep the signatures
keep <- drug_drug$X_id
down.gs.filter <- down.gs__[names(down.gs__) %in% keep]
up.gs.filter <- up.gs__[names(up.gs__) %in% keep]

down.gs.filter <- down.gs.filter[order(drug_drug$X_id)]
up.gs.filter <- up.gs.filter[order(drug_drug$X_id)]

names(down.gs.filter) <- paste("L1000CDS2.down", drug_drug$sig_id, sep = ".") #change to a different naming, more meaninghful system
names(up.gs.filter) <- paste("L1000CDS2.up", drug_drug$sig_id, sep = ".") #change to a different naming, more meaninghful system

drug_drug$PDN_name <- paste("L1000CDS2", drug_drug$sig_id, sep = ".")


L1000CDS2.gs <- c(up.gs.filter, down.gs.filter)
length(up.gs.filter)
length(down.gs.filter)
length(L1000CDS2.gs)

# save(L1000CDS2.gs, file ="L1000CDS2.subset.gs")
# save(L1000CDS2.gs, file ="L1000CDS2.subset.2700.gs")
```

keep selected drugs
```{r eval=FALSE, include=FALSE}
#keep the signatures
x <- selected_drug
keep <- x$X_id
down.gs.filter <- down.gs__[names(down.gs__) %in% keep]
up.gs.filter <- up.gs__[names(up.gs__) %in% keep]

down.gs.filter <- down.gs.filter[order(x$X_id)]
up.gs.filter <- up.gs.filter[order(x$X_id)]

names(down.gs.filter) <- paste("L1000CDS2.down", x$sig_id, sep = ".") #change to a different naming, more meaninghful system
names(up.gs.filter) <- paste("L1000CDS2.up", x$sig_id, sep = ".") #change to a different naming, more meaninghful system

x$PDN_name <- paste("L1000CDS2", x$sig_id, sep = ".")


L1000CDS2.gs.selected <- c(up.gs.filter, down.gs.filter)
length(up.gs.filter)
length(down.gs.filter)
length(L1000CDS2.gs.selected)

# save(L1000CDS2.gs.selected, file ="L1000CDS2.selected.subset.gs")
# save(L1000CDS2.gs, file ="L1000CDS2.subset.2700.gs")
```


```{r}
library(pathprint)
data("pathprint.Hs.gs")

version <- "pathprint.L1000CDS2.subset"
load("L1000CDS2.subset.gs")
load("DPD.Union.2017.Hs.gs")
DPD.Hs.gs.new <- DPD.Hs.gs
DPD.Hs.gs.Pathway <- DPD.Hs.gs.new[grep("Pathway\\.", names(DPD.Hs.gs.new))]
DPD.Hs.gs.Static <- DPD.Hs.gs.Pathway[grep("Static Module", names(DPD.Hs.gs.Pathway))]
head(DPD.Hs.gs.Pathway)
names(DPD.Hs.gs.Static) <- sub("`", "", names(DPD.Hs.gs.Static))
names(DPD.Hs.gs.Static) <- gsub("\\{|\\(", "", names(DPD.Hs.gs.Static))
names(DPD.Hs.gs.Static) <- gsub("\\}|\\)", "", names(DPD.Hs.gs.Static))
names(DPD.Hs.gs.Static) <- gsub(" |,", "_", names(DPD.Hs.gs.Static))
head(names(DPD.Hs.gs.Static))
head(DPD.Hs.gs.Static)

DPD.Hs.gs.L1000CDS2 <- c(DPD.Hs.gs.Pathway, L1000CDS2.gs)
length(DPD.Hs.gs.L1000CDS2)

# saveRDS(DPD.Hs.gs.L1000CDS2, file= paste("DPD.Hs.gs.PDN.", version, ".RDS", sep=""))
# saveRDS(L1000CDS2.gs, file = "L1000CDS.Hs.gs")

version <- "MSigDB.L1000CDS2.subset"
load("L1000CDS2.subset.gs")
MSigDB.Hs.gs <- readRDS("MSigDB.Hs.gs")
MSigDB.Hs.gs.L1000CDS2 <- c(MSigDB.Hs.gs, L1000CDS2.gs)
length(MSigDB.Hs.gs.L1000CDS2)

# saveRDS(MSigDB.Hs.gs.L1000CDS2, file= paste(version, ".RDS", sep=""))

#made this version for RA, AD, PD relevant cells and drugs
#19/02/2019
version <- "MSigDB.L1000CDS2.selected.staticmod.subset"
# can be any subset of LINCS CDS2, this one is from above, enriched for RA, PD and AD things
load("L1000CDS2.selected.subset.gs")
MSigDB.Hs.gs <- readRDS("MSigDB.Hs.gs")
MSigDB.Hs.gs.L1000CDS2.selected <- c(MSigDB.Hs.gs, DPD.Hs.gs.Static, L1000CDS2.gs.selected)
length(MSigDB.Hs.gs.L1000CDS2.selected)
head(MSigDB.Hs.gs.L1000CDS2.selected)

# this file is currently used
# saveRDS(MSigDB.Hs.gs.L1000CDS2.selected, file= paste(version, ".RDS", sep=""))
```
subset to p value
```{r eval=FALSE, include=FALSE}
hist(cds_id_pvals$pval, breaks = 100)
head(up.gs.filter)
head(cds_id_pvals)
head(drug_drug)

dim(drug_drug)
drug_pval <- drug_drug[drug_drug$X_id %in% cds_id_pvals$ObjectId[cds_id_pvals$pval < 0.01],]
dim(drug_pval)
drug_pval <- drug_drug[drug_drug$X_id %in% cds_id_pvals$ObjectId[cds_id_pvals$pval < 0.001],]
dim(drug_pval)

```


subset the gene sets only on the ones we want. 
```{r eval=FALSE, include=FALSE}
#keep the signatures
keep <- drug_drug$X_id
down.gs.filter <- down.gs__[names(down.gs__) %in% keep]
up.gs.filter <- up.gs__[names(up.gs__) %in% keep]

down.gs.filter <- down.gs.filter[order(drug_drug$X_id)]
up.gs.filter <- up.gs.filter[order(drug_drug$X_id)]

names(down.gs.filter) <- paste("L1000CDS2.down", drug_drug$sig_id, sep = ".") #change to a different naming, more meaninghful system
names(up.gs.filter) <- paste("L1000CDS2.up", drug_drug$sig_id, sep = ".") #change to a different naming, more meaninghful system

drug_drug$PDN_name <- paste("L1000CDS2", drug_drug$sig_id, sep = ".")


L1000CDS2.gs <- c(up.gs.filter, down.gs.filter)
length(up.gs.filter)
length(down.gs.filter)
length(L1000CDS2.gs)

# save(L1000CDS2.gs, file ="L1000CDS2.subset.gs")
```


```{r}
library(pathprint)
data("pathprint.Hs.gs")

version <- "pathprint.L1000CDS2.subset"

load("DPD.Union.2017.Hs.gs")
DPD.Hs.gs.new <- DPD.Hs.gs
DPD.Hs.gs.Pathway <- DPD.Hs.gs.new[grep("Pathway\\.", names(DPD.Hs.gs.new))]

DPD.Hs.gs.L1000CDS2 <- c(DPD.Hs.gs.Pathway, L1000CDS2.gs)
length(DPD.Hs.gs.L1000CDS2)

# saveRDS(DPD.Hs.gs.L1000CDS2, file= paste("DPD.Hs.gs.PDN.", version, ".RDS", sep=""))
# saveRDS(L1000CDS2.gs, file = "L1000CDS.Hs.gs")

version <- "MSigDB.L1000CDS2.subset"
load("L1000CDS2.subset.gs")
MSigDB.Hs.gs <- readRDS("MSigDB.Hs.gs")
MSigDB.Hs.gs.L1000CDS2 <- c(MSigDB.Hs.gs, L1000CDS2.gs)

# saveRDS(MSigDB.Hs.gs.L1000CDS2, file= paste(version, ".RDS", sep=""))

length(MSigDB.Hs.gs)
```
